new_analses

### 2021-08-10 data analysis/new_analyses.Rmd
as

>>>>

# GAM try

```{r}
data4 %>% 
  filter(!is.na(doyh)) %>% 
  summarise(min(doyh), max(doyh))
```

```{r}
library(mgcv)

data2 %>% 
    mutate(gender_A = case_when(
    gender == "m" ~ 0,
    gender == "f" ~ 1,
    TRUE ~ NA_real_
  )) %>% 
  filter(!is.na(gender)) %>% 
  mutate_if(is_character, as.factor) %>% 
  filter(month == "June") -> june
```

```{r}
gam_doy1 <- gam(gender_A ~ 
                 s(doyh, by = crop) + crop + 
                 s(location, by = year, bs = "re"), 
               family = "binomial", method = "REML", 
               data = june)
summary(gam_doy1)
plogis(coef(gam_doy1)[1])

plot(gam_doy1, residuals = FALSE, pch = 1, ylim = c(0,1), cex = 1,
     trans = plogis,  
     seWithMean = TRUE,
     shade = TRUE, 
     shift = coef(gam_doy)[1],
     shade.col = "lightgreen")

mgcv::predict.gam(gam_doy1, type = "response", se.fit = TRUE)
```

```{r}
visreg(gam_doy2, "doyh", "crop", 
       gg= TRUE, overlay = TRUE,
       scale="response",
       jitter=TRUE, 
#       rug=2
#       fill.par = list(fill = c("#30123bFF"), alpha = 0.1),
#       line=list(color = c("#30123bFF"), alpha = 0.1)
       ) +
  labs(x = "Day of year", y = " Probability (%)") +
  facet_grid(scales = "free") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_viridis_d(option = "C") +
  scale_fill_viridis_d(option = "C", alpha = 0.05) +
  annotate("text", x = 205, y = 0.90, label = "Second cohort",
            size = 5, color = 1) +
  theme_test() 
```

```{r}
gam1 <- gam(gender_A ~ 
                  s(doyh, by = crop) + 
                  s(height, by = crop) + 
                  s(weight, by = crop) + 
                  month +
                  s(location, by = year, bs = "re"), 
               family = "binomial", method = "REML", 
               data = data4)

gam2 <- gam(gender_A ~ 
                  s(doyh) + 
                  s(height, by = crop) + 
                  s(weight, by = crop) + 
#                  month +
                  s(location, by = year, bs = "re"), 
               family = "binomial", method = "REML", 
               data = data4)
plot(gam2, residuals = FALSE, pch = 1, ylim = c(0,1), cex = 1,
     trans = plogis,  
     seWithMean = TRUE,
     shade = TRUE, 
     shift = coef(gam_doy)[1],
     shade.col = "lightgreen")
anova(gam1, gam2, test = "F")
summary(gam2)
```

```{r}
gam_doy2 <- gam(gender_A ~ 
                 s(height, by = crop) + 
                  s(height, by = crop) + 
                  s(weight, by = crop) + 
                 s(location, by = year, bs = "re"), 
               family = "binomial", method = "REML", 
               data = data4 %>% filter(month == "July"))
summary(gam_doy2)
plogis(coef(gam_doy2)[2])

plot(gam_doy2, residuals = FALSE, pch = 1, ylim = c(0,1), cex = 1,
     trans = plogis,  
     seWithMean = TRUE,
     shade = TRUE, 
     shift = coef(gam_doy)[1],
     shade.col = "lightgreen")

mgcv::predict.gam(gam_doy2, type = "response", se.fit = TRUE)
```

```{r}
visreg(gam_doy2, "doyh", "crop", 
       gg= TRUE, overlay = TRUE,
       scale="response",
       jitter=TRUE, 
#       rug=2
#       fill.par = list(fill = c("#30123bFF"), alpha = 0.1),
#       line=list(color = c("#30123bFF"), alpha = 0.1)
       ) +
  labs(x = "Day of year", y = " Probability (%)") +
  facet_grid(scales = "free") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_viridis_d(option = "C") +
  scale_fill_viridis_d(option = "C", alpha = 0.05) +
  annotate("text", x = 205, y = 0.90, label = "Second cohort",
            size = 5, color = 1) +
  theme_test() 
```

```{r}
data3 %>% 
  ggplot(aes(x = doyh, y = gender_A)) +
  geom_point(alpha = 0.1, aes(color = crop)) +
  geom_emoji(data = cohortf1, aes(x = x, y = y), emoji = "2640") +
  geom_emoji(data = cohortm1, aes(x = x, y = y), emoji = "2642") +
  geom_smooth(aes(color = crop), 
              method = "glm", 
              se = TRUE, alpha = 0.05,
              method.args=list(family="binomial"),
              stat = "smooth") +
  theme_test(base_family = "roboto") +
  facet_grid(~month) +
#  scale_color_manual(values = c(2,1)) +
#  scale_fill_manual(values = c(2,1)) +
  scale_color_viridis_d(option = "C") +
  scale_fill_viridis_d(option = "C", alpha = 0.05) +
  scale_x_continuous(limits = c(170, 260), 
                     breaks = seq(170, 260, 15)) +
  scale_y_continuous( breaks = seq(0, 1, by = 0.2)) +
  labs(x = "Day of year", y = NULL) +
  geom_text(data = first, mapping = aes(x = x, y = y), label = first$label,
            size = 10, color = 1) +
  geom_text(data = second, mapping = aes(x = x, y = y), label = second$label,
            size = 10, color = 2) +
  theme(legend.position = "none",
        axis.title = element_markdown(size = 35),
        axis.text = element_markdown(size = 25),
        strip.text = element_markdown(face = "bold", size = 30)) -> pl_doyh
#  xlim(175, 270)

ggsave("figures/fig.png", width = 9, height = 4)
```
